EqPropNEAT\\Extending NEAT with equlibrium propagation

### 2022-10-03 paper.tex
first paragraph of intro

>>>>

\section{Introduction}
\IEEEPARstart{T}{he} process of designing neural network models always involves deciding on a particular network architecture. In order to avoid both overfitting as well as subpar prediction quality, the right amount of network complexitiy has to be found for a particular learning task. Over the years, a great amount of experience has accomulated regarding this decision, however these rules are more about empirical know-how, than proven theorems.
